Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-09-02 paper/galsize_paper.tex
Finished draft of 4.2

%%%%%%%%  units  %%%%%%%%
\newcommand{\kpc}{{\rm kpc}}
\newcommand{\mpc}{{\rm Mpc}}

@@

@@

In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales. We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a highly non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.

@@

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
\caption{
{\bf Two-point clustering data used to validate the fiducial model.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}. We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass. The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels. The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}). 
}
\label{fig:clustering_ratio_upshot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
\caption{
{\bf Clustering provides tight constraints on the relative sizes of centrals and satellites.} 
Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles. The successful prediction of our fiducial model, in which satellite galaxies neither contract nor puff up after infall, places tight constraints on satellite-specific physical processes, which must be either negligible or conspiratorially produce little-to-no size change after accretion. 
}
\label{fig:satellites}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

>>>>

%%%%%%%%  units  %%%%%%%%
\newcommand{\kpc}{{\rm kpc}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\msun}{M_\odot}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
\caption{
{\bf Two-point clustering predictions of the fiducial model.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}. We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass. The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels. The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}). 
}
\label{fig:clustering_ratio_upshot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales. We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.

@@

In this section we explore how post-infall changes in satellite $\rhalf$ manifest in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall size evolution of satellites.

In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall. The simple interpretation of this assumption is that, in a statistical sense, the size of satellite galaxies is determined by its history as a central galaxy, and that post-infall physics leaves no distinct imprint on satellite $\rhalf.$

Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
\caption{
{\bf Clustering tightly constrains satellite-specific size evolution.} 
Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles. The successful prediction of our fiducial model, in which satellite galaxies neither contract nor puff up after infall, places tight constraints on satellite-specific physical processes, which must be either negligible or conspiratorially produce little-to-no size change after accretion. 
}
\label{fig:satellites}
\end{figure}
%-----------------------------------------------------------------------------------------------------

Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves). The difference between the small-scale clustering of the two models is stark: the assumption that $\rhalf$ decreases after infall leaves a strong imprint on the $\rhalf-$dependence of $\wproj(\rproj),$ such that small galaxies cluster {\em much} more strongly relative to large galaxies, particularly for disk-dominated systems with $\mstar\approx10^{10}\msun.$

The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}. We refer the reader to \S\ref{subsec:satellite_discussion} for further discussion of the physical implications of this result.

@@

@@

\subsection{Physical Interpretation for Satellites}
\label{subsec:satellite_discussion}
